Figures for conference paper

### 2019-04-30 conference figures.Rmd

@@

load("Output/catalogues_best_model.RDATA")
load("Output/data_pillar_1.Rdata")
load("Output/d_text.RDATA")
load("Output/df_logLike_catalogue.RDATA")
load("Output/CV.RDATA")

@@

```{r TM}
d     <- best_lda
gamma <- best_lda$Gamma
beta  <- best_lda$Beta
```

@@

  select(`Course ID`, `Course Title`, Department = department, word) 
```

@@

  labs(title = "Model Selection", subtitle = str_c("The maximum-likelihood model has ", max_LL, " topics"), x = "Number of Topics", y = "Log-Likelihood") +

@@

```{r plot_beta}
plot_beta <- function(topic = 1, sub = NULL, resize_factor = 1){

@@

    labs(title = str_c("Main Terms of ", top),
         subtitle = sub,
         x = "Terms",
         y = "Beta"
    )

@@

```{r fig_beta}
# topic 1: engineering",
plot_beta(1, sub = "Topic 1 corresponds to the theme of engineering")
# topic 9: computer science, topic 
# Topic 20: psychology
# topic 25: history
# topic 26: literature 
```

@@

```{r plot_gamma}
plot_gamma <- function(course = "COR1002", sub = NULL, course_title = course){

@@

    labs(title    = str_c("Main Topics of Course ", course_title),
         subtitle = sub,
         x = "Topics",
         y = "Gamma"
         )

@@

```{r fig_gamma}
plot_gamma("HUM1014", sub = "HUM1014 is dominated by topics 43 (philosophy) and 26 (literature)", course_title = "HUM1014 Great Novels 1850 - Present")

@@

plot_beta(43, sub = "Theme of philosophy", resize_factor = resize_factor)

plot_beta(26, sub = "Theme of literature", resize_factor = resize_factor)
```

# Topic Expertise
```{r}
transcript <- tibble(Course    = paste("Course", 1:3),
                     Grade     = c(6  , 9  , 2.5))

gamma <- tibble(Course    = paste("Course", 1:3),
                `Topic 1` = c(0  , 0.2, 0.6),
                `Topic 2` = c(0.4, 0.2, 0.3),
                `Topic 3` = c(0  , 0.2, 0  ),
                `Topic 4` = c(0.4, 0.2, 0.1),
                `Topic 5` = c(0.2, 0.2, 0  ))

@@

# Plot
df1 %>% 
  ggplot(aes(x = Topic, y = contribution, fill = Course)) +
  geom_col() +
  labs(x = "Topics", y = "Topic Expertise", title = "Course Contribution towards Topic Expertise")

@@

# CV
```{r}
fit_lasso %>%
  ggplot(aes(y = cv_error, group = 1)) +
  geom_boxplot() +
  theme(axis.ticks.x = element_line(color = "white"),
        axis.text.x = element_text(color = "white"),
        panel.border = element_rect(color = "white"),
        panel.grid = element_line(color = "white")
        ) +

  labs(title = "Distribution of Prediction Error", y = "Cross-Validation \n Mean Absolute Error")

ggsave(filename = str_c("CV.jpeg"), path = output_folder,
         width = plot_width/1.9, height = plot_height/1.2)

>>>>

# Set up

@@

load("Output/app_model.RDATA")
load("Output/data_pillar_1.Rdata")
load("Output/d_text.RDATA")
load("Output/df_logLike_catalogue.RDATA")
load("Output/CV.RDATA")

@@

```{r TM}
gamma <- app_model$Gamma[[1]]
beta  <- app_model$Beta[[1]]
```

@@

  select(`Course ID`, `Course Title`, Department = department, word) %>%

@@

  labs(title = NULL, subtitle = NULL, x = "Number of Topics", y = "Log-Likelihood") +

@@

```{r plot_beta}
plot_beta <- function(topic = 1, resize_factor = 1){

@@

    labs(title = str_c("Topic ", topic),
         x = "Terms",
         y = "Beta"
         )

@@

```{r fig_beta}
plot_beta(1)
```

@@

```{r plot_gamma}
plot_gamma <- function(course = "COR1002"){

@@

    labs(title = course,
         x = "Topics",
         y = "Gamma"
         )

@@

```{r fig_gamma}
plot_gamma("COR1004")

@@

plot_beta(4, resize_factor = resize_factor)
plot_beta(19, resize_factor = resize_factor)
```

# Topic Expertise
```{r}
courses <- paste("Course", 1 : 3)

transcript <- tibble(Course    = courses,
                     Grade     = c(6  , 9  , 2.5))

gamma <- tibble(Course    = courses,
                `Topic 1` = c(0  , 0.2, 0  ),
                `Topic 2` = c(0.7, 0.2, 0.4),
                `Topic 3` = c(0.2, 0.2, 0.2),
                `Topic 4` = c(0.1, 0.2, 0.1),
                `Topic 5` = c(0  , 0.2, 0.2))

@@

# Plot
df1 %>% 
  ggplot(aes(x = Topic, y = contribution, fill = Course)) +
  geom_col() +
  labs(x = "Topics", y = "Topic Expertise")

@@

# CV
```{r}
fit_lasso %>%
  ggplot(aes(y = cv_error, group = 1)) +
  geom_boxplot() +
  theme(axis.ticks.y = element_line(color = "white"),
        axis.text.y  = element_text(color = "white"),
        panel.border = element_rect(color = "white"),
        panel.grid   = element_line(color = "white")
        ) +

  labs(y = "Cross-Validation Mean Absolute Error") +
  coord_flip()

ggsave(filename = str_c("CV.jpeg"), path = output_folder,
         width = plot_width/1.5, height = plot_height/3.5)
